Access to Food in Chicago: \\ a Hierarchical Perspective

### 2016-11-22 paper.tex
Added presentation

We tried to gather data on crimes and use that information in the model, however the available dataset for crimes in chicago is rather large ($>$1 GB) and we didn't have time to finish extracting features from that model. We hypothesized that food deserts were more likely to be in high crime areas.

@@

$$ y_{ij} = \text{logit}^{-1}\left( \alpha + X_{B}\beta_{B} + \epsilon_{ij} \right) $$

Where $\epsilon_{ij} \sim N(0, \sigma^2)$

@@

$$ y_{i} = \text{logit}^{-1}\left( \alpha + X_{B}\beta_{B} +  \gamma_j + \epsilon_{ij} \right) $$

Where $\epsilon_i \sim N(0, \sigma^2)$

@@

$$ y_{i} = \text{logit}^{-1}\left( \alpha_{j[i]} + X_{B}\beta_{B} +  \epsilon_i \right) $$

Where $\epsilon_i \sim N(0, \sigma^2)$ and $\alpha_j \sim N(0, \sigma^2_\alpha)$

@@

$$ y_{i} = \text{logit}^{-1}\left( \alpha_{j[i]} + X_{B}\beta_{B} +  \epsilon_i \right) $$

Where $\epsilon_i \sim N(0, \sigma^2)$ and $\alpha_j \sim N(X_N \beta_N, \sigma^2_\alpha)$

@@

@@

>>>>

@@

$$ y_{ij} = \text{logit}^{-1}\left( \alpha + X_{B}\beta_{B}  \right) $$

% Where $\epsilon_{ij} \sim N(0, \sigma^2)$

@@

$$ y_{i} = \text{logit}^{-1}\left( \alpha + X_{B}\beta_{B} +  \gamma_j  \right) $$

% Where $\epsilon_i \sim N(0, \sigma^2)$

@@

$$ y_{i} = \text{logit}^{-1}\left( \alpha_{j[i]} + X_{B}\beta_{B}  \right) $$

Where % $\epsilon_i \sim N(0, \sigma^2)$ and
$\alpha_j \sim N(\mu_\alpha, \sigma^2_\alpha)$

@@

$$ y_{i} = \text{logit}^{-1}\left( \alpha_{j[i]} + X_{B}\beta_{B}  \right) $$

Where % $\epsilon_i \sim N(0, \sigma^2)$ and
$\alpha_j \sim N(X_N \beta_N, \sigma^2_\alpha)$

@@

The variance ratio $\frac{\sigma^2_alpha}{\sigma^2_y}$ in the hierarchical model is approximately 2.97 which means that for a neighborhood of more than 1/2.97 $\approx$ .33 city blocks, the within neighborhood model is more informative. This indicates that pooling and hierarchical structure may not be completely effective.

@@

Additionally: the model isn't great and much more work would have to be done in order to make it useful.
